### 2017-05-18 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1746 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1748 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1749 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
	title="Example of a simple R markdown document with subfigures", 		
	author='Patrick Brown',
	bibliography = bibFile,
	geometry='margin=1in',
	csl = system.file('src','apa-no-doi-no-issue.csl', package='Pmisc'),
	css = system.file('src','article.css', package='Pmisc')
)
```

# Introduction

@lindgren2011explicit is a very good paper, but Figure [@fig:aplot] is dull.

$$
\begin{aligned}
f(x) = &x + \int_0^\infty \exp(-\theta u^2) du\\
\rho(x) = & \sum_i x^i
\end{aligned}
$$

>>>>

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
  title="Example of a simple R markdown document with subfigures", 		
  author='Patrick Brown',
  bibliography = bibFile,
  geometry='margin=1in'
)
```

# Introduction {#sec:intro}

@lindgren2011explicit is a very good paper, but Figure [@fig:aplot] is dull.
There are some formulas in this document, from ([@eq:myeqn]) we can see
nothing useful.  If you are unsure of which Section we are in, be aware that
this is Section [@sec:intro].

$$
\begin{aligned}
f(x) = &x + \int_0^\infty \exp(-\theta u^2) du\\
\rho(x_1 \ldots x_N) = & \sum_i x^i
\end{aligned}
$$ {#eq:myeqn}

Now some plots.
